---
title: "homework2"
author: "jeonghyeon lee"
date: "March 22, 2017"
output:
  html_document: default
---

### Setup

Import libraries
```{r}
library(ggplot2)
library(ggmap)
library(chorddiag)
```

Read csv files
```{r}
tashu = read.csv("tashu.csv")
station = read.csv("station.csv")
```

### Top 10 tashu station

1. Count tashu station usage
```{r}
rent_count = data.frame(table(tashu$RENT_STATION))
return_count = data.frame(table(tashu$RETURN_STATION))
```

2. Merge rent_count, return_count group by station number
```{r}
sum_count <- merge(x = rent_count, y = return_count, by = c("Var1"), all = TRUE)
```

3. Sum rent, return count
```{r}
sum_count$Sum <- rowSums(sum_count[,c("Freq.x", "Freq.y")], na.rm = TRUE)
```

4. Sort descending by sum count
```{r}
sum_count <- sum_count[order(-sum_count$Sum),]
```

5. Select top 10 station
```{r}
top10_station <- sum_count[1:10,]
```

6. Top 10 tashu station frequency bar graph
```{r}
ggplot(data = top10_station, aes(x = Var1, y = Sum/1000, fill = Var1)) + 
  geom_bar(stat="identity") + 
  xlab("Station Number") + 
  ylab("Frequency (thousand)") + 
  ggtitle("Top 10 tashu station frequency") + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Tashu frequency map

1. Merge station, sum_count group by station number
```{r}
station_merge <- merge(station, sum_count, by.x = c("NUMBER"), by.y = c("Var1"))
```

2. Get geocode(lon : 127.3845, lat : 36.35041)
```{r}
daejon_gc <- geocode("Daejon")
daejon_cent <- as.numeric(daejon_gc)
```

3. Tashu station frequency map
```{r}
ggmap(get_googlemap(center = daejon_cent, scale = 1,maptype = "roadmap",zoom = 13)) + 
  geom_point(x = station_merge$LON, y = station_merge$LAT, colour = "red", 
             size = station_merge$Sum/30000, data = station_merge, alpha = 0.5) +
  xlab("Lon") +
  ylab("Lat") +
  ggtitle("Tashu station frequency map") + 
  theme(plot.title = element_text(hjust = 0.5))
```

### Top 20 tashu trace

1. Count trace usage
```{r}
trace_count <- data.frame(table(tashu$RENT_STATION, tashu$RETURN_STATION))
```

2. Sort descending by trace count
```{r}
trace_count <- trace_count[order(-trace_count$Freq),]
```

3. Select top 20 trace
```{r}
top20_trace <- trace_count[1:20,]
```

4. Top 20 tashu trace graph
```{r}
qplot(Var1, Var2, data = top20_trace, size = Freq) + 
  xlab("Rent station") +
  ylab("Return station") +
  ggtitle("Top 20 tashu trace") + 
  theme(plot.title = element_text(hjust = 0.5))
```

## Top 20 tashu trace chord diagram
```{r}
top20_trace_matrix <- matrix(0, 108, 108)

for(i in 1:20) {
  from <- top20_trace[i,1]
  to <- top20_trace[i,2]
  freq <- top20_trace[i,3]
  top20_trace_matrix[from,to] <- freq
}

haircolors <- head(station$NAME, 108)
dimnames(top20_trace_matrix) <- list(have = haircolors, prefer = haircolors)
chorddiag(top20_trace_matrix, groupnamePadding = 40, groupnameFontsize = 10)
```